Dark Control:\\ Towards a Unified Account of Default Mode Function\\ by Markov Decision Processes

### 2017-12-05 paper/paper.tex
Add second part of the memory aspects of MDP in DMN with addition of Pezzulo 2011 ref.

@@

From the perspective of a model-free RL agent,
\textit{inference} in the human brain reduces to
generalization of
policy and value computations from sampled experiences to
successful action choices and reward predictions in future states.
As such,
plasticity in the DMN arises naturally.
If an agent behaving optimally in a certain environment moves
to new, yet unexperienced environment, reward prediction errors will
largely increase.
This feedback will lead to adaptation of policy considerations
and value estimations until the intelligent system converges to a
new steady state of optimal action decisions in a volatile world.

>>>>

\paragraph*{On implicit and explicit memory in the current model.}
Markov Processes are memoryless but this is possible mathematically to artificially insert the previous states of such model into the current state. While this may partially account for implicit memory at the behavioral level, it does not explain the underlying implementation at the neurophysiological level nor accounts for the explicit part of memory.
First, it is possible to incorporate explicit memory capacities into the MDP.

 We address this question in the paper by clarifying what memory retrieval would mean in the current account. In fact, implicit memory-based processing is already present in our MDP account of DMN function. It occurs in 3 three different forms: a) the action policy, b) the value function $\textemdash$as both of these are a result/product of the past$\textemdash$ and c) the deep architecture with many non-linear links in the hierarchical connections as realized by biological neural networks. Indeed, we reason about the brain has deep neural networks that present an implicit form of information compression obtained from life experience. This memory traces are implicitly stored in the neural machinery and can be retrieve as a form of Knowledge by simulation of action rather than accessed as a stored explicit representation \citep{pezzulo2011grounding}. The neural processes in the hippocampus can be seen as MCMC sampling from a formal statistical level but those memory recall are also the basis for scene construction processes across time-scales such as in the semantic hypothesis \citep{schacter2007remembering}. In a complementary way, neural encoding of reward information is not limited to value but incorporates specific information about the identity of the reward outcome, the predictive stimulus, or the action necessary to obtain the reward \citep{kahnt2017decade}.

@@

From the perspective of a model-free RL agent,
\textit{prediction} in the human brain reduces to
generalization of
policy and value computations from sampled experiences to
successful action choices and reward predictions in future states.
As such,
plasticity in the DMN arises naturally.
If an agent behaving optimally in a certain environment moves
to new, yet unexperienced environment, reward prediction errors will
largely increase.
This feedback will lead to adaptation of policy considerations
and value estimations until the intelligent system converges to a
new steady state of optimal action decisions in a volatile world.
